A Data-Driven Framework for Neural Field Modeling

### 2011-01-18 ltx/first_order_framework/LaTeX_Manuscript.tex
added online algorithm to the extension

A further extension of the framework is to allow for the algorithm to learn online. The estimation framework that we have presented is inherently a batch algorithm designed to operate after data has been collected. A simple real-time implementation can be achieved using the UKF and an online recursive LS estimator \cite{Ljung1999}. Other more sophisticated approaches that may be used in a real-time estimation scheme include the incremental EM algorithm \cite{Neal1998}, and the stepwise EM \citep{Sato2000,Cappe2009}.

>>>>

\parham{The estimation framework that we have presented is inherently a batch algorithm designed to operate after data has been collected. A further extension of the framework is to allow for the algorithm to learn online. A filter which is designed to be implemented in an online setting can be used in place of the smoother along with an online parameter estimator to update the parameter after a new observation arrived. A simple real-time implementation can be achieved using the UKF (instead of the URTSS) and an online recursive LS estimator \cite{Ljung1999}.}

%  A simple real-time implementation can be achieved using the UKF and an online recursive LS estimator \cite{Ljung1999}.

% Other more sophisticated approaches that may be used in a real-time estimation scheme include the incremental EM algorithm \cite{Neal1998}, and the stepwise EM \citep{Sato2000,Cappe2009}.
